---
title             : "Neuroticism's association with other factors: The revenge"
shorttitle        : "Everyone's Neurotic"

author: 
  - name          : "Diego"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Catrina"
    affiliation   : "1,2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"
  - name          : "Ian"
    affiliation   : "3"
    
affiliation:
  - id            : "1"
    institution   : "Millie University"
  - id            : "2"
    institution   : "Krusty's Hamburger School"
  - id            : "3"
    institution   : "Smooth Hacker University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

csl               : "apa (2).csl"
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")

```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
```

# Introduction

Neuroticism means you will die young and alone - ha ha ha [@widiger2017neuroticism]. Is Neuroticism negatively correlated with the other four Big Five personalty dimensions? THE WORLD WANTS TO KNOW!!!!

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

```{r, warning=FALSE, echo=FALSE, message=FALSE}
library(psych)
library(lavaan)
library(semPlot)
library(semTools)

data(bfi)

#Recode A1, C4, C5, E1, E2, O2, O5
library(dplyr)
bfi.recoded<- bfi %>% 
  mutate_at(vars(c(1,9,10,11,12,22,25)), 
            ~as.numeric(recode(.,
                               "6"=1,
                               "5"=2, 
                               "4"=3,
                               "3"=4,
                               "2"=5,
                               "1"=6))) 

#Scale Scores
bfi.recoded$a<- rowMeans(bfi.recoded[1:5])
bfi.recoded$c<- rowMeans(bfi.recoded[6:10])
bfi.recoded$e<- rowMeans(bfi.recoded[11:15])
bfi.recoded$n<- rowMeans(bfi.recoded[16:20])
bfi.recoded$o<- rowMeans(bfi.recoded[21:25])

#reclassify gender
bfi.recoded$gender<- as.factor(as.character(bfi.recoded$gender))

```

```{r corrmatrix, caption="Correlation Table", echo=FALSE}
#cor(bfi.recoded[29:33], use="complete.obs")

r <- corx::corx(bfi.recoded[,c(29:33)],
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$`=mean, `$SD$`=sd))

papaja::apa_table(r$apa,
                  escape=FALSE,
                  note="Neuroticism ROCKS!!!",
                  caption = "Bunch of correlations among personality traits")
```

# Results

```{r}
multreg <- lm(n ~ a+o+c+e, bfi.recoded)

reportreg <- apa_print(multreg)
```

The correlations are presented in Table \@ref(tab:corrmatrix). Regression with Neuroticism as a DV and the other four traits as predictors returned `r reportreg$statistic$modelfit`.

```{r neuroplot, fig.cap="scatter of Conscientiousness and Neuroticism"}
library(ggplot2)

plot <- ggplot(bfi.recoded, aes(x=c, y=n, color=gender)) + geom_point() + geom_jitter() + papaja::theme_apa() + geom_smooth(method=lm, se=TRUE)
  
plot
```

You can see associations between C and N in Figure \@ref(fig:neuroplot)  

```{r funky, fig.cap="Don't have a seizure"}
#graph
library(tidyverse)
library(treemap)

data_bfi<-bfi.recoded%>%select(A1:O5)%>%pivot_longer(cols=c(1:25), names_to="Factor")
data_bfi$Dimension<-substr(data_bfi$Factor, 1, 1)

treemap(data_bfi, index=c("Dimension","Factor"),     vSize="value", type="index",
 
    fontsize.labels=c(15,12),                # size of labels. Give the size per level of aggregation: size for group, size for subgroup, sub-subgroups...
    fontcolor.labels=c("white","orange"),    # Color of labels
    fontface.labels=c(2,1),                  # Font of labels: 1,2,3,4 for normal, bold, italic, bold-italic...
    bg.labels=c("transparent"),              # Background color of labels
    align.labels=list(
        c("center", "center"),
        c("right", "bottom")
        ),                                   # Where to place labels in the rectangle?
    overlap.labels=0.5,                      # number between 0 and 1 that determines the tolerance of the overlap between labels. 0 means that labels of lower levels are not printed if higher level labels overlap, 1  means that labels are always printed. In-between values, for instance the default value .5, means that lower level labels are printed if other labels do not overlap with more than .5  times their area size.
    inflate.labels=F,                        # If true, labels are bigger when rectangle is bigger.
 
)

```

You can see dizzying colors in Figure \@ref(fig:funky)  

```{r queenbee, fig.cap="Ian says this wins"}

df <- as.data.frame(cbind(bfi.recoded[26:33]))
df<-na.omit(df)
df <- df[ -c(2,3) ]
means<-aggregate(df,by=list(df$gender),mean)
means<-aggregate(df,by=list(df$gender),mean)
means <- means[ -c(2) ]

library(reshape2)
means.long<-melt(means,id.vars="Group.1")

library(ggplot2)
ggplot(means.long,aes(x=variable,y=value,fill=factor(Group.1)))+
  geom_bar(stat="identity",position="dodge")+
  scale_fill_discrete(name="Gender",
                      breaks=c(1, 2),
                      labels=c("Male", "Female"))+
  xlab("BFI")+ylab("Average") + papaja::theme_apa()
```

A barplot is available in Figure \@ref(fig:queenbee)

# Discussion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
