---
title: "Untitled"
format: dashboard
server: shiny
---

## Shiny Documents

This Quarto document is made interactive using Shiny. Interactive documents allow readers to modify parameters and see the results immediately. Learn more about Shiny interactive documents at <https://quarto.org/docs/interactive/shiny/>.

## Inputs and Outputs

![](https://th.bing.com/th/id/R.9dbdb528fef91228583c3485e39ec60e?rik=f6yhMH4k5Hq0AA&pid=ImgRaw&r=0)

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change. This demonstrates how a standard R plot can be made interactive:

```{r}
sliderInput("bins", "Number of bins:", 
            min = 1, max = 50, value = 30)

downloadLink('downloadData', 'Download')

plotOutput("distPlot")

data <- as.data.frame(faithful[, 2])

## https://stackoverflow.com/questions/74947736/how-to-download-quarto-pdf-reports-from-r-shiny-application
```

```{r}
#| context: server

output$distPlot <- renderPlot({
   x <- faithful[, 2]  # Old Faithful Geyser data
   bins <- seq(min(x), max(x), length.out = input$bins + 1)
   hist(x, breaks = bins, col = 'darkgray', border = 'white',
        xlab = 'Waiting time to next eruption (in mins)',
        main = 'Histogram of waiting times')
})

output$downloadData <- downloadHandler(
   filename = function() {
     paste('data-', Sys.Date(), '.csv', sep='')
   },
   content = function(con) {
     write.csv(data, con)
   }
 )
```
